Fourmile state variables

### 2025-05-02 state_vars.Rmd
looking at burn and unburn HRU state vars

flow <- both %>%
  select(date, 
         source, 
         outRG1,
         outRG2,
         outRD1, 
         outRD2,
         source)

rd1_model <- aov(outRD2 ~ source, data = flow)
summary(rd1_model)

>>>>

unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'unburn') %>%
  filter(year == 2011)

burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
  mutate(date = mdy(time),
         year = year(date),
         type = 'burn') %>%
  filter(year == 2011)

both <- bind_rows(unburn, burn)

# interception
inter <- both %>%
  dplyr::select(date, type, interception)

ggplot(inter,
       aes(x=date,,
           y=interception,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# swe
swe <- both %>%
  dplyr::select(date, type, snowTotSWE)

ggplot(swe,
       aes(x=date,,
           y=snowTotSWE,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# swe
p <- both %>%
  dplyr::select(date, type, precip)

ggplot(p,
       aes(x=date,,
           y=precip,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# surface runoff
runoff <- both %>%
  dplyr::select(date, type, outRD1)

ggplot(runoff,
       aes(x=date,,
           y=outRD1,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# interflow
interflow <- both %>%
  dplyr::select(date, type, outRD2)

ggplot(interflow,
       aes(x=date,,
           y=outRD2,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

gw <- both %>%
  dplyr::select(date, type, outRG1)

ggplot(gw,
       aes(x=date,,
           y=outRG1,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# dps
dps <- both %>%
  dplyr::select(date, type, actDPS)

ggplot(dps,
       aes(x=date,,
           y=actDPS,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# mps
mps <- both %>%
  dplyr::select(date, type, soilSatMPS)

ggplot(mps,
       aes(x=date,,
           y=soilSatMPS,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# lps
lps <- both %>%
  dplyr::select(date, type, soilSatLPS)

ggplot(lps,
       aes(x=date,,
           y=soilSatLPS,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)

# soil sat
soilsat <- both %>%
  dplyr::select(date, type, soilSat)

ggplot(soilsat,
       aes(x=date,,
           y=soilSat,
           color=type)) +
  geom_line() +
  theme_bw(base_size=20)
